Learning with misspecified models: Overconfidence and Stereotypes

### 2023-09-12 Paper/draft.Rmd
session1

## The Self-Serving Bayesian

@@

In the example and for the seed that was drawn and fixed throughout, the models make different predictions.

>>>>

## The Self-Serving Updater

@@

Because the different models apply only under certain conditions, I split the predictions into two groups; the dogmatic and the 
switcher constitute the first group, and the bayesian and self-serving updater are the second group. the predictions of group 1
apply only in cases where $(\theta, \omega)$ are such that there is a self-defeating equilibrium. This is because whenever 
there is no self defeating equilibria, the dogmatic model does not apply. On the other hand, the theories of group 2 apply to all
possible combinations of the parameters. Hence, these theories can be tested and differentiated within a broader set of 
observations.

It is also important to note that since the predictions of the model are asymptotic and probabilistic, the predictions that are made 
for the particular example that was taken to the lab depend strongly on the realized sequence of signals. Because the randomness has 
been controlled for and kept fixed across sessions, for every parametrization $(\theta, \omega)$ there is a unique optimal path 
for each of the models. I present the predictions made by this particular realization of the seed.\footnote{The seed that was drawn 
at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
the tasks in the experiment, as well as for drawing the outcomes from the gambles.}

## Dogmatic and Switcher

The cases in which we can apply these two theories are the five self-defeating equilibria from the data generating process in the 
example. From these and with the seed that was drawn, the models make different predictions in 4 cases. \footnote{the fifth 
self-defeating equilibrum is such that the likelihood ratio does not go above 1 and thus the switcher is indistinguishable from 
the dogmatic agent.}

## Bayesian and self-attribution updater

### 2023-09-12 Paper/draft.tex
session1

\title{Learning with misspecified models: Overconfidence and
Stereotypes}
\author{Jimena Galindo}
\date{September 07, 2023}

@@

\hypertarget{the-self-serving-bayesian}{%
\subsection{The Self-Serving Bayesian}\label{the-self-serving-bayesian}}

@@

By including self-confirming equilibria, the example captures the forces
from each of the updating mechanisms discussed in the previous section
and allows for direct comparison of all the theories. For realizations
of \((\theta, \omega)\) for which there are self-confirming equilibria,
the dogmatic agent will fall into the trap whereas the switcher will be
able to escape it. Similarly, an agent with self-attribution bias will
update their beliefs differently from an unbiased Bayesian, leading them
to choose different gambles. I exploit such cases in order to test which
model is a better fit for how subjects behave in a laboratory
experiment.
\footnote{because the setting does not match that of @Heidhues2018, there will be situationf for which the theory 
does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
belief persists or not for the switcher, depends highly on the realized history of signals that he gets.}
In what follows I explain the details of how this example was
implemented in the lab.

@@

>>>>

\title{Learning with misspecified models: Overconfidence and
Stereotypes}
\author{Jimena Galindo}
\date{September 12, 2023}

@@

\hypertarget{the-self-serving-updater}{%
\subsection{The Self-Serving Updater}\label{the-self-serving-updater}}

@@

By including self-confirming equilibria, the example captures the forces
from each of the updating mechanisms discussed in the previous section
and allows for direct comparison of all the theories. For realizations
of \((\theta, \omega)\) for which there are self-confirming equilibria,
the dogmatic agent will fall into the trap whereas the switcher will be
able to escape it. Similarly, an agent with self-attribution bias will
update their beliefs differently from an unbiased Bayesian, leading them
to choose different gambles. I exploit such cases in order to test which
model is a better fit for how subjects behave in a laboratory
experiment.
\footnote{because the setting does not match that of Heidhues et al. [2018], there will be situationf for which the theory 
does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
belief persists or not for the switcher, depends highly on the realized history of signals that he gets.}
In what follows I explain the details of how this example was
implemented in the lab.

@@

\hypertarget{predictions}{%
\section{Predictions}\label{predictions}}

Because the different models apply only under certain conditions, I
split the predictions into two groups; the dogmatic and the switcher
constitute the first group, and the bayesian and self-serving updater
are the second group. the predictions of group 1 apply only in cases
where \((\theta, \omega)\) are such that there is a self-defeating
equilibrium. This is because whenever there is no self defeating
equilibria, the dogmatic model does not apply. On the other hand, the
theories of group 2 apply to all possible combinations of the
parameters. Hence, these theories can be tested and differentiated
within a broader set of observations.

It is also important to note that since the predictions of the model are
asymptotic and probabilistic, the predictions that are made for the
particular example that was taken to the lab depend strongly on the
realized sequence of signals. Because the randomness has been controlled
for and kept fixed across sessions, for every parametrization
\((\theta, \omega)\) there is a unique optimal path for each of the
models. I present the predictions made by this particular realization of
the seed.\footnote{The seed that was drawn 
at the beginning of session 1 was 3452. The same seed was used for all sessions. It is used both for drawing $\omega$ for each of 
the tasks in the experiment, as well as for drawing the outcomes from the gambles.}

\hypertarget{dogmatic-and-switcher}{%
\subsection{Dogmatic and Switcher}\label{dogmatic-and-switcher}}

The cases in which we can apply these two theories are the five
self-defeating equilibria from the data generating process in the
example. From these and with the seed that was drawn, the models make
different predictions in 4 cases. \footnote{the fifth 
self-defeating equilibrum is such that the likelihood ratio does not go above 1 and thus the switcher is indistinguishable from 
the dogmatic agent.}

\hypertarget{bayesian-and-self-attribution-updater}{%
\subsection{Bayesian and self-attribution
updater}\label{bayesian-and-self-attribution-updater}}
